Stage-Splitting a Modal Language

### 2014-08-12 paper/splitting.tex
fixing a typo kayvon noticed

The splitting algorithm comprises two judgments, $\splitonesym$ and $\splittwosym$.
For both, the input is a term in \lang, and the output is two terms in \langmono, an
unstaged language.  The grammar for \langmono is given in \ref{fig:monoGrammar}.  It has no
staging features (we say that implicitly it has only one stage), and it is untyped.  
Modulo these differences, \langmono has all of the same features as \lang, 
although this is a matter of taste
\footnote{Since \lang is untyped, we could encode everything with just functions.}.

>>>>

The splitting algorithm comprises two judgments, $\splitonesym$ and $\splittwosym$.
For both, the input is a term in \lang, and the output is two terms in \langmono, an
unstaged language.  The grammar for \langmono\ is given in \ref{fig:monoGrammar}.  It has no
staging features (we say that implicitly it has only one stage), and it is untyped.  
Modulo these differences, \langmono\ has all of the same features as \lang, 
although this is a matter of taste
\footnote{Since \langmono\ is untyped, we could encode everything with just functions.}.
